\documentclass{resume}
\usepackage[left=0.65in,top=0.5in,right=0.65in,bottom=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

%--- Color theme ----------------------------------------------------------
\definecolor{accent}{RGB}{0,70,127}          % professional navy

%--- Colored name ---------------------------------------------------------
\makeatletter
\renewcommand{\printname}{%
  \begingroup
    \hfil{\namesize\bf\color{accent}\@name}\hfil
    \nameskip\break
  \endgroup
}
\makeatother

%--- Colored section header + rule ----------------------------------------
\renewenvironment{rSection}[1]{%
  \sectionskip
  {\color{accent}\MakeUppercase{\bf #1}}%
  \sectionlineskip
  {\color{accent}\hrule}%
  \begin{list}{}{\leftmargin=1.5em}%
  \item[]
}{%
  \end{list}
}

%--- Summary block (no list indent) ----------------------------------------
\newenvironment{summaryBlock}{%
  \sectionskip
  {\color{accent}\MakeUppercase{\bf Professional Summary}}%
  \sectionlineskip
  {\color{accent}\hrule}%
  \smallskip\noindent\ignorespaces
}{%
  \par\medskip
}

%--- Filled bullets, tighter spacing --------------------------------------
\renewenvironment{rSubsection}[4]{%
  {\bf #1} \hfill {#2}%
  \ifthenelse{\equal{#3}{}}{}{%
    \\
    {\em #3} \hfill {#4}%
  }\smallskip
  \begin{list}{\small\textbullet}{\leftmargin=1.5em}%
    \itemsep -0.5em \vspace{-0.5em}
}{%
  \end{list}%
  \vspace{0.3em}
}

%--- Contact --------------------------------------------------------------
\name{Lening Li}
\address{Boston, MA, USA}
\address{%
  +1\,(774)\,823\,2639 \;$|$\;
  \href{mailto:leningli@outlook.com}{leningli@outlook.com} \;$|$\;
  \href{https://lening.li}{lening.li} \;$|$\;
  \href{https://linkedin.com/in/lening-li}{linkedin.com/in/lening-li}%
}

\begin{document}

%--- PROFESSIONAL SUMMARY -------------------------------------------------
\begin{summaryBlock}
MBA candidate at Carnegie Mellon Tepper with a Ph.D.\ in Robotics Engineering
and 5+ years leading technology teams at enterprise scale.
Deep domain expertise in AI/ML, autonomous systems, and software infrastructure
--- the core of the TMT landscape.
Track record of managing complex, multi-stakeholder projects from scoping
through delivery under strict deadlines, coaching junior engineers, and
communicating technical value to non-technical stakeholders.
Seeking to apply quantitative rigor, TMT domain fluency, and
entrepreneurial drive to investment banking deal execution.
\end{summaryBlock}

%--- EDUCATION ------------------------------------------------------------
\begin{rSection}{Education}

{\bf Carnegie Mellon University, Tepper School of Business} \hfill Pittsburgh, PA \\
MBA \hfill {\em Expected May 2028}
\begin{list}{\small\textbullet}{\leftmargin=1.5em}
  \itemsep -0.5em \vspace{-0.5em}
  \item Coursework: Corporate Finance, Valuation, Financial Accounting, Statistics \& Data Analysis
\end{list}

\smallskip
{\bf Worcester Polytechnic Institute} \hfill Worcester, MA \\
Ph.D.\ in Robotics Engineering \hfill Dec.\ 2022 \\
M.S.\ in Robotics Engineering \hfill May 2018 \\
M.S.\ in Computer Science \hfill May 2016

\smallskip
{\bf Harbin Institute of Technology} \hfill China \\
B.S.\ in Computer Science, \emph{Summa Cum Laude} (Top 5\% of class) \hfill Jul.\ 2014 \\
B.A.\ in English Language \& Literature \hfill Jul.\ 2014

\end{rSection}

%--- PROFESSIONAL EXPERIENCE ----------------------------------------------
\begin{rSection}{Professional Experience}

\begin{rSubsection}{Senior Software Engineer}{Oct.\ 2022 -- Present}{Symbotic}{Wilmington, MA}
\item Manage cross-functional project delivery across engineering, controls, and operations teams --- coordinating timelines, resolving blockers, and ensuring milestones are met under aggressive deadlines.
\item Lead technical scoping, design reviews, and stakeholder presentations for multi-agent AI systems deployed across fleets of thousands of autonomous robots at enterprise-scale warehouse clients.
\item Identified and championed a new path-planning initiative that reduced fleet deadlock incidents, securing buy-in from product leadership and driving the project from concept through production deployment.
\item Translate complex technical concepts into clear executive-level communications for product leadership and external partners, driving alignment across diverse audiences.
\item Mentor and develop junior engineers; define project goals, track performance, and provide structured feedback to accelerate team output.
\end{rSubsection}

\begin{rSubsection}{Robotic Lab Advisor}{Dec.\ 2025 -- Present}{Harvard University}{Cambridge, MA}
\item Advise graduate research teams on project scoping, technical strategy, and milestone execution --- bridging academic research and commercial deployment.
\item Built and managed end-to-end AI training infrastructure on cloud GPU platforms, overseeing budgets, vendor selection, and resource allocation.
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer}{Oct.\ 2021 -- Aug.\ 2022}{Berkshire Grey}{Bedford, MA}
\item Led a cross-functional initiative to redesign robotic perception and manipulation pipelines, managing scope and delivery across hardware and software teams.
\item Drove end-to-end system performance improvements by identifying bottlenecks, proposing solutions, and managing implementation --- cutting system latency and boosting throughput.
\end{rSubsection}

\begin{rSubsection}{President, Graduate Student Government}{Jan.\ 2019 -- May\ 2020}{Worcester Polytechnic Institute}{Worcester, MA}
\item Led WPI's graduate student government, managing competing stakeholder interests across students, faculty, senior administration, and the Board of Trustees.
\item Escalated student housing concerns to the Board of Trustees and served on the Provost Search Committee, demonstrating institutional influence and structured advocacy.
\item Appointed by the university president to formally represent the graduate student body in institutional governance and strategic decision-making.
\end{rSubsection}

\end{rSection}

%--- TMT DOMAIN EXPERTISE -------------------------------------------------
\begin{rSection}{TMT Domain Expertise}
\begin{list}{\small\textbullet}{\leftmargin=1.5em}
  \itemsep -0.5em \vspace{-0.5em}
  \item \textbf{AI / Machine Learning:} Deep fluency in the AI value chain --- reinforcement learning, generative AI (VLA models), computer vision, and enterprise ML deployment.
  \item \textbf{Robotics \& Autonomous Systems:} Hands-on experience across the full robotics stack (perception, planning, control), including DARPA-funded programs and production autonomous fleets.
  \item \textbf{Enterprise Software \& Infrastructure:} Built distributed real-time systems at scale; experienced with cloud GPU infrastructure, multi-agent architectures, and system integration.
\end{list}
\end{rSection}

%--- DEAL-RELEVANT SKILLS -------------------------------------------------
\begin{rSection}{Relevant Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
Financial Analysis   & Valuation, Financial Modeling, DCF, Comps (via MBA coursework) \\
Quantitative         & Ph.D.-level Statistics, Optimization, Stochastic Modeling, Data Analysis \\
Communication        & Executive Presentations, Technical Writing, Stakeholder Management \\
Project Management   & Multi-workstream Coordination, Timeline Management, Risk Mitigation \\
Languages            & English (Fluent), Chinese (Native)
\end{tabular}
\end{rSection}


%--- PUBLICATIONS \& RECOGNITION ------------------------------------------
\begin{rSection}{Publications \& Recognition}
\textbf{12 peer-reviewed publications} in top AI, robotics, and control venues including
ICRA, IJCAI (15\% acceptance rate), CDC, ACC, and IEEE Transactions on Automation Science
and Engineering. \\[3pt]
\href{https://scholar.google.com/citations?user=KWUJ10wAAAAJ}{Google Scholar}\\[3pt]
\textbf{Alex F.\ Backlin Fund Scholarship}, Worcester Polytechnic Institute, 2021
\end{rSection}

\end{document}
