\documentclass{resume}
\usepackage[left=0.65in,top=0.5in,right=0.65in,bottom=0.55in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

%--- Color theme ----------------------------------------------------------
\definecolor{accent}{RGB}{0,70,127}          % professional navy

%--- Colored name ---------------------------------------------------------
\makeatletter
\renewcommand{\printname}{%
  \begingroup
    \hfil{\namesize\bf\color{accent}\@name}\hfil
    \nameskip\break
  \endgroup
}
\makeatother

%--- Colored section header + rule ----------------------------------------
\renewenvironment{rSection}[1]{%
  \sectionskip
  {\color{accent}\MakeUppercase{\bf #1}}%
  \sectionlineskip
  {\color{accent}\hrule}%
  \begin{list}{}{\leftmargin=1.5em}%
  \item[]
}{%
  \end{list}
}

%--- Summary block (no list indent) ----------------------------------------
\newenvironment{summaryBlock}{%
  \sectionskip
  {\color{accent}\MakeUppercase{\bf Professional Summary}}%
  \sectionlineskip
  {\color{accent}\hrule}%
  \smallskip\noindent\ignorespaces
}{%
  \par\medskip
}

%--- Filled bullets, tighter spacing --------------------------------------
\renewenvironment{rSubsection}[4]{%
  {\bf #1} \hfill {#2}%
  \ifthenelse{\equal{#3}{}}{}{%
    \\
    {\em #3} \hfill {#4}%
  }\smallskip
  \begin{list}{\small\textbullet}{\leftmargin=1.5em}%
    \itemsep -0.5em \vspace{-0.5em}
}{%
  \end{list}%
  \vspace{0.3em}
}

%--- Contact --------------------------------------------------------------
\name{Lening Li}
\address{Boston, MA, USA}
\address{%
  +1\,(774)\,823\,2639 \;$|$\;
  \href{mailto:leningli@outlook.com}{leningli@outlook.com} \;$|$\;
  \href{https://lening.li}{lening.li} \;$|$\;
  \href{https://linkedin.com/in/lening-li}{linkedin.com/in/lening-li}%
}

\begin{document}

%--- PROFESSIONAL SUMMARY -------------------------------------------------
\begin{summaryBlock}
AI/ML engineer with a Ph.D.\ in Robotics Engineering and 5+ years of industry experience
delivering production AI systems at enterprise scale. Expertise spans reinforcement learning,
game-theoretic AI, and generative AI --- including end-to-end VLA model training on GPU cloud.
Track record leading cross-functional AI initiatives with solutions deployed across fleets of
thousands of robots. Pursuing an MBA at Carnegie Mellon Tepper to complement technical depth
with strategic business leadership.
\end{summaryBlock}

%--- CORE COMPETENCIES ----------------------------------------------------
\begin{rSection}{Core Competencies}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} l }
AI/ML             & Reinforcement Learning, Deep Learning, Optimal Control, Game Theory \\
Generative AI     & Vision-Language-Action (VLA) Models, PyTorch \\
Systems           & Multi-Agent Systems, Distributed AI, Real-Time Decision Making \\
Cloud             & Nebius GPU Cloud \\
Languages         & English (Fluent), Chinese (Native)
\end{tabular}
\end{rSection}

%--- PROFESSIONAL EXPERIENCE ----------------------------------------------
\begin{rSection}{Professional Experience}

\begin{rSubsection}{Robotics Lab Advisor}{Dec.\ 2025 -- Present}{Harvard University}{Cambridge, MA}
\item Built end-to-end generative AI training pipelines for Vision-Language-Action (VLA) models on Nebius GPU cloud, covering distributed training infrastructure and model evaluation.
\item Consult graduate AI research teams on algorithm design, system architecture, and evaluation methodology --- bridging academic research and production deployment.
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer}{Oct.\ 2022 -- Present}{Symbotic}{Wilmington, MA}
\item Architected and deployed production multi-agent AI decision systems in C++ for coordinated fleets of thousands of autonomous warehouse robots.
\item Designed real-time AI planning pipelines meeting strict latency requirements at enterprise scale; improved fleet robustness through state estimation and fault-tolerant behavior architectures.
\item Led cross-functional initiatives across systems, controls, and operations teams to deliver integrated AI solutions in a high-stakes production environment.
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer}{Oct.\ 2021 -- Aug.\ 2022}{Berkshire Grey}{Bedford, MA}
\item Led development of computer vision and manipulation AI enabling robust grasping of novel, previously unseen objects (ROS, C++, Python).
\item Cut end-to-end latency by overhauling inter-process communication and AI inference pipelines for real-time robotic picking systems.
\end{rSubsection}

\end{rSection}

%--- REPRESENTATIVE PROJECTS ----------------------------------------------
\begin{rSection}{Representative Projects}

\begin{rSubsection}{DARPA SI3-CMD}{Jan.\ 2019 -- Aug.\ 2020}{Researcher}{Worcester, MA}
\item Served as technical lead for an industry-partnered DARPA project with Scientific Systems Company Inc.\ (SSCI), delivering AI research outcomes on contract.
\item Developed a game-theoretic AI framework for strategic deceptive planning; improved mission success probability by exploiting information asymmetry within a formal hypergame model.
\end{rSubsection}

\begin{rSubsection}{DARPA Robotics Challenge}{Aug.\ 2014 -- May\ 2015}{Researcher}{Worcester, MA}
\item Designed motion planning and human-robot interaction algorithms for the Boston Dynamics Atlas humanoid robot; WPI-CMU team ranked \textbf{7th out of 24} at the DARPA Robotics Challenge Finals.
\end{rSubsection}

\begin{rSubsection}{Optimal Control and Reinforcement Learning for Stochastic Systems under Temporal Logic Specifications}{Aug.\ 2016 -- Aug.\ 2022}{Ph.D.\ Researcher}{Worcester, MA}
\item Developed a principled framework translating probabilistic temporal logic specifications into chance-constrained control problems with formal satisfaction guarantees.
\item Proposed scalable, model-free reinforcement learning algorithms for continuous stochastic systems, improving sample efficiency and enabling real-world deployment.
\end{rSubsection}

\end{rSection}

%--- EDUCATION ------------------------------------------------------------
\begin{rSection}{Education}

{\bf Carnegie Mellon University, Tepper School of Business} \hfill Pittsburgh, PA \\
MBA \hfill {\em Expected May 2028}

\smallskip
{\bf Worcester Polytechnic Institute} \hfill Worcester, MA \\
Ph.D.\ in Robotics Engineering \hfill Dec.\ 2022 \\
M.S.\ in Robotics Engineering \hfill May 2018 \\
M.S.\ in Computer Science \hfill May 2016

\smallskip
{\bf Harbin Institute of Technology} \hfill China \\
B.S.\ in Computer Science, \emph{Summa Cum Laude} (Top 5\% of class) \hfill Jul.\ 2014

\end{rSection}

%--- LEADERSHIP -----------------------------------------------------------
\begin{rSection}{Leadership}

\begin{rSubsection}{President, Graduate Student Government}{Jan.\ 2019 -- May\ 2020}{Worcester Polytechnic Institute}{Worcester, MA}
\item Led WPI's graduate student government, managing competing stakeholder interests across students, faculty, senior administration, and the Board of Trustees.
\item Escalated student housing concerns to the Board of Trustees and served on the Provost Search Committee, demonstrating institutional influence and structured advocacy.
\end{rSubsection}

\end{rSection}

%--- PUBLICATIONS & RECOGNITION -------------------------------------------
\begin{rSection}{Publications \& Recognition}
\textbf{12 peer-reviewed publications} in top AI, robotics, and control venues including
ICRA, IJCAI (15\% acceptance rate), CDC, ACC, and IEEE Transactions on Automation Science
and Engineering. \\[3pt]
\href{https://scholar.google.com/citations?user=KWUJ10wAAAAJ}{Google Scholar}\\[3pt]
\textbf{Alex F.\ Backlin Fund Scholarship}, Worcester Polytechnic Institute, 2021
\end{rSection}

\end{document}
