\documentclass{resume}
\usepackage[left=0.7in,top=0.6in,right=0.7in,bottom=0.6in]{geometry}
\usepackage{url}

%----------------------------------------------------------------------------------------
%	CONTACT
%----------------------------------------------------------------------------------------
\name{Lening Li}
\address{Boston, MA, USA}
\address{+1 (774) 823 2639 | leningli@outlook.com | \url{https://lening.li}}

\begin{document}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Robotics Lab Advisor}{Dec. 2025 -- Present}{Harvard University}{Cambridge, MA}
\item Guide robotics research projects with focus on learning-based planning, control, and reproducible experimental methodology.
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer}{Oct. 2022 -- Present}{Symbotic}{Wilmington, MA}
\item Designed and shipped production multi-agent path-planning and coordination algorithms in C++ for warehouse robot fleets of thousands.
\item Improved fleet robustness through advances in control design, state estimation, and fault-tolerant behavior architectures.
\item Optimized real-time decision pipelines to meet strict latency constraints across thousands of concurrent autonomous robots.
\end{rSubsection}

\begin{rSubsection}{Senior Software Engineer}{Oct. 2021 -- Aug. 2022}{Berkshire Grey}{Bedford, MA}
\item Led development of perception and manipulation algorithms enabling robust grasping of novel, previously unseen SKUs (ROS, C++, Python).
\item Cut end-to-end system latency by overhauling inter-process communication and execution pipelines.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Carnegie Mellon University} \hfill Pittsburgh, PA \\
MBA Candidate \hfill {\em Expected May 2028}

{\bf Worcester Polytechnic Institute} \hfill Worcester, MA \\
Ph.D. in Robotics Engineering \\
M.S. in Robotics Engineering | M.S. in Computer Science

{\bf Harbin Institute of Technology} \hfill China \\
B.S. in Computer Science (Summa Cum Laude) | B.A. in English Language \& Literature

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
Programming Languages: & C/C++, Python, MATLAB \\
Robotics \& Learning: & Motion Planning, Optimal Control, Reinforcement Learning \\
Robotic Systems: & ROS, Distributed Robotic Systems, Real-Time C++ on Linux \\
Machine Learning: & PyTorch, TensorFlow \\
Languages: & English (Fluent), Chinese (Native)
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	ADDITIONAL
%----------------------------------------------------------------------------------------
\begin{rSection}{Additional}
12 publications in top robotics, control, and AI venues (ICRA, CDC, ACC, IJCAI, IEEE T-ASE) \\
Google Scholar: \url{https://scholar.google.com/citations?user=KWUJ10wAAAAJ} \\
GitHub: \url{https://github.com/leelening} \\
Member, IEEE Robotics and Automation Society
\end{rSection}

\end{document}
